\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{multicol}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{flushleft}
    {\huge Alexandre Ait Ettajer} \\
\end{flushleft}
\begin{multicols}{2}
    \raggedright
    \href{mailto:alexandre.aitettajer@gmail.com}{alexandre.aitettajer@gmail.com} \\
    +1 (281) 435-9481 \\
    Brookline, MA \\
    
    \columnbreak
    
    \raggedleft
    \href{https://www.alexandreae.com}{alexandreae.com} \\
    GitHub: \href{https://github.com/aiteta}{Aiteta} \\
    LinkedIn: \href{https://www.linkedin.com/in/alexandre-ait-ettajer-65740b170/}{alexandre-ait-ettajer}
\end{multicols}

\begin{minipage}[t]{0.65\textwidth}
    % Summary
    \section*{SUMMARY}
    Software engineer with 5+ years of experience building full-stack web applications and APIs. Passionate about clean code, scalable architecture, and improving developer experience.\\

    % Experience
    \section*{EXPERIENCE}
    {\Large Senior Associate Software Engineer} \\
    \textbf{The MathWorks, Inc.} \\
    05/2024 -- Present \textbar\ Natick, MA
    \begin{itemize}[leftmargin=*]
        \item Built web apps with React, Node.js, and PostgreSQL.
        \item Wrote unit tests with Jest and integration tests using Cypress.\\
    \end{itemize}

    {\Large Associate Software Engineer} \\
    \textbf{The MathWorks, Inc.} \\
    04/2023 -- 04/2024 \textbar\ Natick, MA
    \begin{itemize}[leftmargin=*]
        \item Built web apps with React, Node.js, and PostgreSQL.
        \item Wrote unit tests with Jest and integration tests using Cypress.\\
    \end{itemize}

    {\Large Engineering Development Group Associate} \\
    \textbf{The MathWorks, Inc.} \\
    05/2022 -- 03/2023 \textbar\ Natick, MA
    \begin{itemize}[leftmargin=*]
        \item Built web apps with React, Node.js, and PostgreSQL.
        \item Wrote unit tests with Jest and integration tests using Cypress.
    \end{itemize}
    
    % Education
    \section*{EDUCATION}
    {\Large Master of Science in Computer Science} \\
    \textbf{The University of Texas at Austin} \\
    GPA: 3.5 / 4.0 \textbar\ 08/2023 -- Present \textbar\ Austin, TX\\

    {\Large Bachelor of Science in Computer Science} \\
    \textbf{Rensselaer Polytechnic Institute} \\
    GPA: 3.93 / 4.0 \textbar\ 08/2018 -- 05/2022 \textbar\ Troy, NY\\

    {\Large Bachelor of Science in Aeronautical Engineering} \\
    \textbf{Rensselaer Polytechnic Institute} \\
    GPA: 3.93 / 4.0 \textbar\ \textit{08/2018 -- 05/2022} \textbar\ Troy, NY
\end{minipage}
\hfill
\begin{minipage}[t]{0.32\textwidth}
    % Skills
    \section*{Skills}

    \textbf{Languages:} C++, JavaScript, TypeScript, MATLAB,  \\
    \textbf{Frameworks:} React, Node.js, Express, Flask \\
    \textbf{Tools:} Docker, Git, Postgres, Redis, AWS, GitHub Actions

    % Projects
    \section*{Projects}

    \textbf{BudgetPal} \\
    A personal budgeting web/mobile app with bank integration. Built with React Native, Node.js, PostgreSQL, and Docker.

    \textbf{Canticle for the Doomed} \\
    A GitHub-powered tool for recruiters to find open source developers by language, activity, and location.
\end{minipage}
\end{document}
